Fluent statistical computing interfaces for biological data analysis

### 2020-03-16 Rmd/01-intro.Rmd
short dot points
more dot points

## Visual analytics for dimension reduction and clustering workflows

>>>>

- talking about chapters 3 and 4 here
- having the grammar doesn't impair interoperability, in fact we show it
can be used to glue two different approches
- the long form representation can be taken even further... 
- recasting EDA problems as search, we want to find regions measured along the
genome that display a characteristic of interest, and then link that to raw 
data plots.

## Visual analytics for dimension reduction workflows

- talking about chapter 5
- taking a step back in the last chapter, have been focused on data wrangling
but am now looking the integration of vis and models
- focussed on a common part of EDA as applied to transcriptomics, dimension
reduction workflows
- especially non-linear dr as that has gotten extremely popular
- combining with the tour, we can grasp the trade-off between global and
local views of the data
- user interaction provides ability to dissect the quality of a DR, and
perform cluster oriented tasks
